Model Search in Relational Domains

### 2016-10-23 introduction.tex
missing article
cannot

\emph{Abstract Conflict Driven Clause Learning} (ACDCL)~\cite{dhk2013-popl}
is one such generalisation of CDCL.  The partial satisfying assignments in
CDCL algorithm are generalized to be chosen from a given abstract domain. 
The unit rule is the best abstract transformer, Boolean Constraint
Propagation (BCP) computes a greatest fixed-point over the abstract domain,
decision is dual widening and clause learning can be viewed as synthesising
an abstract transformer for negation.  This enables an ACDCL-based analyser
to refine an imprecise analysis and thus prevents enumeration behaviour. 
ACDCL has so far been instantiated as a decision procedure for
floating-point arithmetic~\cite{DBLP:journals/fmsd/BrainDGHK14} and a
program analyser that reasons using intervals~\cite{tacas12}.  Hence, the
existing ACDCL instances are limited to bounds checking in numerical
programs.

Evidently, the verification of many programs requires more expressive
domains like octagons or equalities or polyhedra.  These domains capture
interesting properties of programs that intervals can not express.  In this
paper, we identify specific modifications to the CDCL algorithm that are
necessary to lift propositional CDCL to relational abstract domains such as
octagons, zones and equalities over numerical variables.
\Omit { To this end, we
present a characterisation of an abstract model search procedure and a
conflict analysis procedure that lift the abstract deduction transformer and
the conflict analysis procedure to relational lattice structures.
}

>>>>

\emph{Abstract Conflict Driven Clause Learning} (ACDCL)~\cite{dhk2013-popl}
is one such generalisation of CDCL.  The partial satisfying assignments in
the CDCL algorithm are generalized to be chosen from a given abstract domain. 
The unit rule is the best abstract transformer, Boolean Constraint
Propagation (BCP) computes a greatest fixed-point over the abstract domain,
decision is dual widening and clause learning can be viewed as synthesising
an abstract transformer for negation.  This enables an ACDCL-based analyser
to refine an imprecise analysis and thus prevents enumeration behaviour. 
ACDCL has so far been instantiated as a decision procedure for
floating-point arithmetic~\cite{DBLP:journals/fmsd/BrainDGHK14} and a
program analyser that reasons using intervals~\cite{tacas12}.  Hence, the
existing ACDCL instances are limited to bounds checking in numerical
programs.

Evidently, the verification of many programs requires more expressive
domains like octagons or equalities or polyhedra.  These domains capture
interesting properties of programs that intervals cannot express.  In this
paper, we identify specific modifications to the CDCL algorithm that are
necessary to lift propositional CDCL to relational abstract domains such as
octagons, zones and equalities over numerical variables.
\Omit { To this end, we
present a characterisation of an abstract model search procedure and a
conflict analysis procedure that lift the abstract deduction transformer and
the conflict analysis procedure to relational lattice structures.
}
